mode_speed_summary

### 2020-11-09 code/trips_analysis/mode_speed_summary.Rmd
add motorcycle speeds to speed distancea analysis

trip <- rbind(bangalore, delhi, vizag, sao_paulo)
trip_walk <- filter(trip, mode=="walk")
trip_bicycle <- trip[trip$mode=="bicycle",]
trip_bus <- trip[trip$mode == "bus",]
trip_car <- trip[trip$mode == "car",]

@@

>>>>

trip <- rbind(bangalore, delhi, vizag, sao_paulo)
trip_walk <- filter(trip, mode=="walk")
trip_bicycle <- trip[trip$mode=="bicycle",]
trip_motorcylce <- trip[trip$mode=="motorcycle",]
trip_bus <- trip[trip$mode == "bus",]
trip_car <- trip[trip$mode == "car",]

@@

## Motorcycling
```{r}
boxplot(speed~mode+city, data = droplevels(trip_bicycle), ylim=c(0, 20))
```
